---
title: "Ebola Cases"
author: "Vanessa Guardado"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

Data Cleaning

```{r}
#Uploading csv file
EbolaCases <- here::here("ebola_data_db_format.csv")
EbolaCases <- read.csv(EbolaCases)

#Reorganize data/ only keep confirmed cases of Ebola Cases by Country and then drop column "Indicator"
library(dplyr)
ConfirmedEbolaCases <- EbolaCases %>% filter(Indicator == "Cumulative number of confirmed Ebola cases")
ConfirmedEbolaCases = subset(ConfirmedEbolaCases, select =  -c(Indicator))

#Change Column Value to Confirmed Cases
colnames(ConfirmedEbolaCases)[3] <- "Confirmed_Cases"

#Separate Date into Month and Year
library(tidyverse)

ConfirmedEbolaCases <- ConfirmedEbolaCases %>% separate(Date, sep ="/", into = c("Month", "Day", "Year"))

#Edit Contry Names
table(ConfirmedEbolaCases$Country, useNA = "always")
ConfirmedEbolaCases$Country[ConfirmedEbolaCases$Country == "Guinea 2"] = "Guinea"
ConfirmedEbolaCases$Country[ConfirmedEbolaCases$Country == "Liberia 2"] = "Liberia"
```

Table Result

```{r}

library(gtsummary)

tbl_summary(ConfirmedEbolaCases,
						by = Country,
						include = c(Country, Year, Confirmed_Cases))
```

Regression Result

```{r}

tbl_uvregression(ConfirmedEbolaCases,
								 y= Confirmed_Cases,
								 include = c(Country, Month),
								 method = lm)

Model1 <- lm(Confirmed_Cases ~ Country +Month,
									data = ConfirmedEbolaCases)

tbl_regression(Model1,
							 intercept = TRUE,
							 label = list(Month ~ "Month of Confirmed Case"))

EbolaTable <- tbl_regression(Model1,
							 intercept = TRUE,
							 label = list(Month ~ "Month of Confirmed Case"))
```

Histogram Figure

```{r}
#| label: fig-hist
#| fig-cap: "Confirmed Ebola Cases" 
hist(ConfirmedEbolaCases$Confirmed_Cases)
```

Inline Stats

```{r}

stats <- list(n= nrow(ConfirmedEbolaCases),
							mean_cases = mean(ConfirmedEbolaCases$Confirmed_Cases))

inline_text(EbolaTable, variable = "Country")
```

Cross Referencing

@fig-hist contains a histogram of total confirmed Ebola Cases

Data consists of probable, and confirmed cases for Ebola Cases from 10 countries during 2014-2016. To simply the data, I just focused on confirmed cases and cleaned up the data before starting. I got the data from one of the links github had and linked it below:

https://data.humdata.org/dataset/ebola-cases-2014
